%% start of file literatur.tex

%% Literaturverzeichnis:
\begin{Literatur}
% TODO nummerierung/reihenfolge literatur anpassen
\bibitem[1]{data_PCM2906}{\textbf{TEXAS INSTRUMENTS:} \href{https://www.ti.com/lit/ds/symlink/pcm2906.pdf}{\emph{Datenblatt PCM2904/PCM2906}}. 2007 \newline [online] 04.03.2022 https://www.ti.com/lit/ds/symlink/pcm2906.pdf}

\bibitem[2]{input}{\textbf{WHITLOCK, Bill:} \emph{A new balanced audio input circuit for maximum common-mode rejection in real-world environments}. Journal of the Audio Engineering Society, 1995, 43. Jg., Nr. 6, S. 454-464.}

\bibitem[3]{phantom}{\textbf{PETROV, Petre Tzv:} \href{https://www.diyrecordingequipment.com/products/hc1}{\emph{5V DC To 48V DC Converter For Phantom Power Supplies}}. 04.03.2021, Electronicsforu. [online] 25.03.2022 https://www.electronicsforu.com/electronics-projects/5v-48v-dc-converter-phantom-power-supplies}

\bibitem[4]{fachkunde}{\textbf{BUMILLER, Horst; et al:} {\emph{Fachkunde Elektrotechnik.}} Haan-Gruiten: Verlag Europa-Lehrmittel, Nourney, Vollmer GmbH \& Company KG, 2020. -ISBN 978-3-808-53791-6. S.} 

\bibitem[5]{tietze} \textbf{U. TIETZE und C. SCHENK:} \textit{Electronic circuits. handbook for design and application.} Heidelberg: Springer, 2015.

\bibitem[6]{litKomb} \textbf{Wikibooks:} (4.1.2021) \textit{LaTeX-Kompendium: Schnellkurs: Erstellen eines Literaturverzeichnisses}. [Online]. Available: \url{https://de.wikibooks.org/wiki/LaTeX-Kompendium:\_Schnellkurs:\_Erstellen\_eines\_Literaturverzeichnisses}


\end{Literatur}

%% end of file literatur.tex